Drake Plan

### 2019-08-19 R/drake_plan_conus.Rmd
drake conus 30days

  # get nearest MODIS cells 
  refgrid = get_ref_grid(),
  # near MODIS cells within 300km
  refsub = get_near_cellsid(conus_aer, refgrid),
  # aeronet sites with cloest MODIS grid
  aer_nearest = get_nearest_cell(conus_aer, refgrid), # Aeronet matched to grid, 174x4
  aer_nearest_2 = remove_site_on_water(aer_nearest), # remove 2 sites on water

  # limit aeronet data by date (aer_btw)
  aer_data = get_stn_data(aod_dir = file_in(aer_files_path)),  # 26171206x56, 11G
  aer_btw = target(sel_data_bytime(aer_data, date_start, date_end),
                   transform = map(date_start = !!date_start, 
                                   date_end = !!date_end,
                                   .id = FALSE)),
  # limit aeronet data by station, could be NEMIA or CONUS 
  sel_aer_region = target(sel_data_bystation(aer_btw, aer_nearest_2),
                      transform = map(aer_btw), .id = FALSE),

@@

  # 3. WPred Join MCD19 -----------------------------------------------------------
  # mcd is the large MCD19 dataset, limit to `refsub`:nearby(300km) when readin to 
  # control total lines, unable to read in all data together, too many rows
  mcd = target(read_mcd19(sat, file_in(mcd19path_CONUS), refsub), transform = map(sat = c("terra", "aqua"))),
  # join is the rolling-joined dataset with aeronet
  join = target(rolling_join(mcd_sat = mcd, aer_data_wPred = wPred),
                transform = cross(mcd, wPred, .id = mcd)),

@@

```{r, eval = F}

future::plan(future::multiprocess)
options(future.globals.maxSize= 100*1024^3) 
make(nemia_plan, cache = ssd_cache,
     parallelism = "future", jobs = 20, memory_strategy = "speed")

>>>>

  # get nearest MODIS cells 
  refgrid = get_ref_grid(),

  # aeronet sites with cloest MODIS grid
  aer_nearest = get_nearest_cell(conus_aer, refgrid), # Aeronet matched to grid, 174x4
  aer_nearest_2 = remove_site_on_water(aer_nearest), # remove 2 sites on water

  # limit aeronet data by date (aer_btw)
  aer_data = get_stn_data(aod_dir = file_in(aer_files_path)),  # 26171206x56, 11G
  aer_btw = target(sel_data_bytime(aer_data, date_start, date_end),
                   transform = map(date_start = !!date_start, 
                                   date_end = !!date_end,
                                   .id = FALSE)),
  # limit aeronet data by station, could be NEMIA or CONUS 
  sel_aer_region = target(sel_data_bystation(aer_btw, aer_nearest_2),
                      transform = map(aer_btw, .id = FALSE)),

  # near MODIS cells within 300km
  refsub = target(get_near_cellsid(conus_aer, sel_aer_region, refgrid),
                  transform = map(sel_aer_region, .id = FALSE)),

@@

  # 3. WPred Join MCD19 -----------------------------------------------------------
  # mcd is the large MCD19 dataset, limit to `refsub`:nearby(300km) when readin to 
  # control total lines, unable to read in all data together, too many rows
  mcd = target(read_mcd19(sat, file_in(mcd19path_CONUS)), transform = map(sat = c("terra", "aqua"))),
  # join is the rolling-joined dataset with aeronet
  join = target(rolling_join(mcd_sat = mcd, aer_data_wPred = wPred),
                transform = cross(mcd, wPred, .id = mcd)),

@@

```{r, eval = F}
make(nemia_plan, cache = ssd_cache)

future::plan(future::multiprocess)
options(future.globals.maxSize= 100*1024^3) 
make(nemia_plan, cache = ssd_cache,
     parallelism = "future", jobs = 20, cache_log_file = TRUE)
